  ---
title: "sprite_scraping"
author: "Michael Rose"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(tidyverse)
library(furrr)

plan(multiprocess)
```

# Final Fantasy 1

```{r}
# grab web pages
ff_1_urls_list <- c("http://www.videogamesprites.net/FinalFantasy1/Party/Before/", 
                    "http://www.videogamesprites.net/FinalFantasy1/Party/After/", 
                    "http://www.videogamesprites.net/FinalFantasy1/NPCs/Individuals/",
                    "http://www.videogamesprites.net/FinalFantasy1/NPCs/Townsfolk/",
                    "http://www.videogamesprites.net/FinalFantasy1/NPCs/Nonhuman/",
                    "http://www.videogamesprites.net/FinalFantasy1/NPCs/Individuals/"
                    )

# set image download directory
img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_1_sprites/"

# Download all the indexed images
img_download_reg <- as_mapper(function(i){
  Sys.sleep(5)
  # state url
  cat(paste0("Now Downloading From: ", i, "\n---------------\n"))
  
  # read html
  ff_url <- read_html(i)
  
  # get images into a list
  ff_images <- ff_url %>% 
    html_nodes("a:nth-child(4) , hr~ a") %>% 
    html_text() %>% as_tibble() %>% 
    filter(str_detect(value, ".gif"))
  
  # download all images 
  for (j in 1:dim(ff_images)[[1]]) {
    cat(paste0("Downloading image ", j, " of ", dim(ff_images)[[1]], " : Image Name: ", ff_images$value[j], "\n"))
    download.file(paste0(i, ff_images$value[j]), paste0(img_dir, ff_images$value[j]), mode = "w", method = "wget", cacheOK = TRUE)
  }
}) %>% possibly(otherwise = NA_real_, quiet = TRUE)

# Download all the non indexed images
img_download_ni <- as_mapper(function(i){
  Sys.sleep(5) 

  # state url
  cat(paste0("Now Downloading From: ", i, "\n---------------\n"))
  
  # read html
  ff_url <- read_html(i)
  
  # get images into a list
  ff_images <- ff_url %>% 
    html_nodes("img") %>%
    html_attr("src") %>% as_tibble() %>% 
    filter(str_detect(value, ".gif"))
  
  # download all images 
  for (j in 1:dim(ff_images)[[1]]) {
    cat(paste0("Downloading image ", j, " of ", dim(ff_images)[[1]], " : Image Name: ", ff_images$value[j], "\n"))
    download.file(paste0(i, ff_images$value[j]), paste0(img_dir, ff_images$value[j]), mode = "w", method = "wget", cacheOK = TRUE)
  }
}) %>% possibly(otherwise = NA_real_, quiet = TRUE)


# download all of the images
future_walk(.x = ff_1_urls_list, .f = img_download_reg)
```

Next we want to convert each animated gif file into a series of png files. For this, I will use a simple bash script: 

```{r, engine = bash. eval = FALSE}
convert *.gif *.png

find . -name \*.png -exec cp {} all_sprite_imgs \;

for file in *png; do mv "$file" "${file:2}"; done
```

# Final Fantasy 2

```{r}
# grab non indexed web pages
ff_2_url_non_index <- "http://www.videogamesprites.net/FinalFantasy2/Party/"

# grab web pages
ff_2_urls_list <- c("http://www.videogamesprites.net/FinalFantasy2/NPCs/Individuals/",
               "http://www.videogamesprites.net/FinalFantasy2/NPCs/Townsfolk/")


# set image download directory
img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_2_sprites/"

# download indexed images
future_walk(ff_2_urls_list, img_download_reg)

# download non indexed images
future_walk(ff_2_url_non_index, img_download_ni)
```

# Final Fantasy 3

```{r}
# grab non indexed web pages
ff_3_url_non_index <- c("http://www.videogamesprites.net/FinalFantasy3/Party/OnionKnight/")

# grab web pages 
ff_3_urls_list <- c(
"http://www.videogamesprites.net/FinalFantasy3/Party/Fire/",
"http://www.videogamesprites.net/FinalFantasy3/Party/Earth/",
"http://www.videogamesprites.net/FinalFantasy3/Party/Status/",
"http://www.videogamesprites.net/FinalFantasy3/Party/Wind/",
"http://www.videogamesprites.net/FinalFantasy3/Party/Water/",
"http://www.videogamesprites.net/FinalFantasy3/Party/Eureka/",
"http://www.videogamesprites.net/FinalFantasy3/NPCs/Individuals/",
"http://www.videogamesprites.net/FinalFantasy3/NPCs/Townsfolk/",
"http://www.videogamesprites.net/FinalFantasy3/NPCs/Nonhuman/"
)

# set image download directory
img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_3_sprites/"

# download indexed
future_walk(ff_3_urls_list, img_download_reg, .progress = TRUE)

# download non indexed 
future_walk(ff_3_url_non_index, img_download_ni, .progress = TRUE)
```

# Final Fantasy 4

```{r}
ff_4_urls_non_index <- c(
  "http://www.videogamesprites.net/FinalFantasy4/Party/Cecil/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Kain/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Rydia/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Rosa/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Edge/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Tellah/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Edward/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Yang/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Palom/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Porom/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/Cid/",
  "http://www.videogamesprites.net/FinalFantasy4/Party/FuSoYa/"
)

ff_4_urls_list <- c(
  "http://www.videogamesprites.net/FinalFantasy4/NPCs/Individuals/",
  "http://www.videogamesprites.net/FinalFantasy4/NPCs/Townsfolk/",
  "http://www.videogamesprites.net/FinalFantasy4/NPCs/Nonhuman/"
)

img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_4_sprites/"

# download indexed
future_walk(ff_4_urls_list, img_download_reg, .progress = TRUE)

# download non indexed
future_walk(ff_4_urls_non_index, img_download_ni, .progress = TRUE)
```

# Final Fantasy 5

```{r}
ff_5_urls_list <- c(
  "http://www.videogamesprites.net/FinalFantasy5/Party/Freelancer/",
  "http://www.videogamesprites.net/FinalFantasy5/Party/Water/",
  "http://www.videogamesprites.net/FinalFantasy5/Party/Earth/",
  "http://www.videogamesprites.net/FinalFantasy5/Party/Wind/",
  "http://www.videogamesprites.net/FinalFantasy5/Party/Fire/",
  "http://www.videogamesprites.net/FinalFantasy5/Party/Other/",
  "http://www.videogamesprites.net/FinalFantasy5/NPCs/Individuals/",
  "http://www.videogamesprites.net/FinalFantasy5/NPCs/Townsfolk/",
  "http://www.videogamesprites.net/FinalFantasy5/NPCs/Nonhuman/"
)


img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_5_sprites/"

# download indexed
future_walk(ff_5_urls_list, img_download_reg, .progress = TRUE)
```

# Final Fantasy 6

```{r}
ff_6_urls_non_index <- c(
  "http://www.videogamesprites.net/FinalFantasy6/Party/Terra/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Locke/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Edgar/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Sabin/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Celes/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Shadow/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Cyan/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Gau/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Setzer/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Mog/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Strago/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Relm/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Gogo/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Umaro/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Vicks/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Banon/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/Ghost/",
  "http://www.videogamesprites.net/FinalFantasy6/Party/GeneralLeo/", 
  "http://www.videogamesprites.net/FinalFantasy6/Party/Imp/"
)

ff_6_urls_list <- c(
  "http://www.videogamesprites.net/FinalFantasy6/NPCs/Returners/",
  "http://www.videogamesprites.net/FinalFantasy6/NPCs/Other/",
  "http://www.videogamesprites.net/FinalFantasy6/NPCs/Nonhuman/",
  "http://www.videogamesprites.net/FinalFantasy6/NPCs/Empire/",
  "http://www.videogamesprites.net/FinalFantasy6/NPCs/Townsfolk/"
)


img_dir <- "~/Desktop/courses/GANs/ff_sprites/ff_6_sprites/"

# download indexed
future_walk(ff_6_urls_list, img_download_reg, .progress = TRUE)

# download non indexed
future_walk(ff_6_urls_non_index, img_download_ni, .progress = TRUE)
```

Placing a copy of all the png files into a pooled directory

```{r, engine = bash, eval = FALSE}
find . -name \*.png -exec cp {} all_sprite_imgs \;
```

Now there is just a bit more cleaning to do. The earlier bash script to break gifs into their constituent frames left us with a bunch of *-file_name.png files. I wish to remove the first two characters. 

```{r, engine = bash, eval = FALSE}
for file in *png; do mv "$file" "${file:2}"; done
```
